---
title: "ESM206_Lab7"
author: "Julia Wilson"
date: "11/8/2021"
output: html_document
---

```{r setup, include = TRUE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

# Attach Packages
library(tidyverse)
library(palmerpenguins)
library(GGally)
library(broom)
library(kableExtra)
library(modelsummary)
```

gg pairs allows you to create a pairs plot which shows bi variant relationships

## Intro to GG pairs

Use GGally::ggpairs() function to create a pairs plot. 

```{r}
ggpairs(penguins)
```


```{r}
penguins %>% 
  select(species, bill_length_mm:body_mass_g) %>% # keeps species and all columns between bill length and body mass 
  ggpairs(aes(color = species)) 

ggplot(data = penguins, aes(x = bill_depth_mm, y = body_mass_g, group = species)) + 
  geom_point(aes(color = species)) +
  geom_smooth(method = "lm")
```

If we miss an important variable ie penguin species, the regression might be completely different! Recognize the important variable using group by. Then there will be a positive relationship between bill depth and body mass. This is called simsons paradox. 

## Multiple Linear Regression - Penguins

Use multiple linear regression to try to understand the relationship between multiple predictor variables and a single continuous outcome variable which will be body mass. 

```{r}
penguin_lm <- lm(body_mass_g ~ flipper_length_mm + bill_depth_mm, data = penguins) #Would like to model body mass as a function of. Always add the data at the end 

# Return just the coefficients: 
penguin_lm 


```

Flipper length coefficient: On average every 1 mm increase in flipper length mm, there is a 51.54 g increase in penguin body mass. If everything else remains constant. 

Allison's: We would expect, on average, a 51.54 g increase in penguin body mass for each 1 mm increase in flipper length, if everything else is constant. 

Use the summary() to get more info: 

```{r}
summary(penguin_lm)
```

Bill depth is not that significant, we would not reject the null hypothesis. A non significant coefficient does not mean you should drop the predictor. The p value alone should not be grounds for adding or removing something from a model. 

R^2 value of 0.7596 means that 76% of variance in penguin body mass is explained by this model, which includes bill depth and flipper length. 

This is not good or bad. It is what it is. 

Clean up data! 

### Use 'broom' functions tidy and glance

Use broom::tidy to get coefficient summary in a data frame. 
Use broom::glance to get the model summary in a data frame. 

```{r}
penguin_lm_tidy <- tidy(penguin_lm)
penguin_lm_tidy

# Refer to only one of these variables
```

Try using in-line code to refer to the bill depth coefficient 

`r round(penguin_lm_tidy$estimate[3])`




