---
title: "ESM206_Lab7"
author: "Julia Wilson"
date: "11/8/2021"
output: html_document
---

```{r setup, include = TRUE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

# Attach Packages
library(tidyverse)
library(palmerpenguins)
library(GGally)
library(broom)
library(kableExtra)
library(modelsummary)
library(stargazer)
```

gg pairs allows you to create a pairs plot which shows bi variant relationships

## Intro to GG pairs

Use GGally::ggpairs() function to create a pairs plot. 

```{r}
ggpairs(penguins)
```


```{r}
penguins %>% 
  select(species, bill_length_mm:body_mass_g) %>% # keeps species and all columns between bill length and body mass 
  ggpairs(aes(color = species)) 

ggplot(data = penguins, aes(x = bill_depth_mm, y = body_mass_g, group = species)) + 
  geom_point(aes(color = species)) +
  geom_smooth(method = "lm")
```

If we miss an important variable ie penguin species, the regression might be completely different! Recognize the important variable using group by. Then there will be a positive relationship between bill depth and body mass. This is called simsons paradox. 

## Multiple Linear Regression - Penguins

Use multiple linear regression to try to understand the relationship between multiple predictor variables and a single continuous outcome variable which will be body mass. 

```{r}
penguin_lm <- lm(body_mass_g ~ flipper_length_mm + bill_depth_mm, data = penguins) #Would like to model body mass as a function of. Always add the data at the end 

# Return just the coefficients: 
penguin_lm 


```

Flipper length coefficient: On average every 1 mm increase in flipper length mm, there is a 51.54 g increase in penguin body mass. If everything else remains constant. 

Allison's: We would expect, on average, a 51.54 g increase in penguin body mass for each 1 mm increase in flipper length, if everything else is constant. 

Use the summary() to get more info: 

```{r}
summary(penguin_lm)
```

Bill depth is not that significant, we would not reject the null hypothesis. A non significant coefficient does not mean you should drop the predictor. The p value alone should not be grounds for adding or removing something from a model. 

R^2 value of 0.7596 means that 76% of variance in penguin body mass is explained by this model, which includes bill depth and flipper length. 

This is not good or bad. It is what it is. 

Clean up data! 

### Use 'broom' functions tidy and glance

Use broom::tidy to get coefficient summary in a data frame. 
Use broom::glance to get the model summary in a data frame. 
These are not necessary, but makes access easier! 

```{r}
penguin_lm_tidy <- tidy(penguin_lm)
penguin_lm_tidy

# Refer to only one of these variables
```

Try using in-line code to refer to the bill depth coefficient 

`r round(penguin_lm_tidy$estimate[3])`

## Broom glance, output will be a data frame but it contains bigger model outputs

```{r}
penguin_lm_glance <- glance(penguin_lm)

penguin_lm_glance
```

## Try another model 

We have thought really hard, done a lit review, consulted w/ experts, deeply explored our data & decided that the 3 most critical variables to include in this model are; 

- flipper length
- species
- sex 


Task: Create a multiple linear regression model using those 3 predictor variables, then take a look at the model outputs & interpret the coefficients with a neighbor.

```{r}
penguin_lm_2 <- lm(body_mass_g ~ flipper_length_mm + species + sex, data = penguins)

penguin_lm_2
```

Adelle penguins are the reference species. Female is the reference level for sex. 

Mass(g) = -365.82 + 20.02(flipper(mm)) - 80.73(chinstrap) + 836.31(Gentoo) + 530.38(Male)

Interpreting Coefficients relevant to a reference level: 
836.26(Gentoo) = if everything else remained constant, then on avg we expect a Gentoo penguin to weight 836.26 g more than an Adelie penguin. 

(-87.63)Chinstrap: Chinstrap penguins would be smaller than Adelie's by -87.63.

Males = If everything else is the same, we expect a male penguin to weigh on average 530g more than a female penguin. 

Predicting mass of chinstrap penguin that was female with flipper length of 180mm: 

Equation: 180 + 1(chin) + 0(gentoo) + 0(male)

Estimate the body mass of a male adelie penguin with 200ml flippers

eq = 200ml + 1(male) + 0(chinstrap) + 0(gentoo)

```{r}
augment(penguin_lm_2)
```

# Use plot() to look at model diagnostics

```{r}
plot(penguin_lm_2)
```

Plot three you want to see constant spread across the duration of the predicted model. 

Assumption of linear regression, independence of residuals. Errors associated with one observation impact errors with another observation. 

- Conceptual understanding and expertise allows me to responsibly determine that penguin species, sex and flipper length are reasonable predictor variable. Make sure to think hard about variables and variable combinations. 

- Diagnostic plots all check out for normality of residuals, homoscedasticity, and no worrisome outliers (<< last one is not an assumption)

What if I wanted to look at a model that used flipper_length, species, sex, and bill length. It would still be an appropriate model! 

Model outputs for papers won't be for a single model. It's usual a combo of predictor variables. 

## Make Output Tables
Using model summary:
```{r}
modelsummary(penguin_lm_2)
```

Using stargazer: create html tables with other output formulas 

```{r, results = "asis"}
stargazer(penguin_lm_2, type = "html") # Check lab report
```








